State Results

### 2023-07-03 reports/priors.Rmd
update figures

tibble(x = seq(0, 1, length = 10^(4)),
       original = with(prior_params, beta_density(x,
                                     mean = s_untested_mean,
                                     sd = s_untested_sd,
                                     bounds = s_untested_bounds)),
       ctis= dbeta(x, shape1=s_untested_shape[1], 
                   shape2=s_untested_shape[2])) %>%
  pivot_longer(c(original,ctis))%>%
   ggplot(aes(x=x, y = value, fill=name)) +
  geom_line(alpha = .8) + 
  geom_ribbon(aes(x=x,ymin=0, ymax=value,fill=name),
              alpha=.6) +
  theme_c(legend.text=element_text(size = 10)) +
  viridis::scale_fill_viridis(discrete=TRUE,
                             option = "rocket", begin=.3,end=.8) +
  labs(x = "Value",
       y = "Probability Density", 
       title = latex2exp::TeX("Definition of Prior for $Pr(S_1|untested)$"),
       fill ='')

>>>>

tibble(x = seq(0, 1, length = 10^(4)),
       original = with(prior_params, beta_density(x,
                                     mean = s_untested_mean,
                                     sd = s_untested_sd,
                                     bounds = s_untested_bounds)),
       ctis= dbeta(x, shape1=s_untested_shape[1], 
                   shape2=s_untested_shape[2])) %>%
  pivot_longer(c(original,ctis))%>%
   ggplot(aes(x=x, y = value, fill=name)) +
  geom_line(alpha = .8) + 
  geom_ribbon(aes(x=x,ymin=0, ymax=value,fill=name),
              alpha=.6) +
  theme_c(legend.text=element_text(size = 10)) +
  viridis::scale_fill_viridis(discrete=TRUE,
                             option = "rocket", 
                             begin=.3,
                             end=.8) +
  labs(x = "Value",
       y = "Probability Density", 
       title = latex2exp::TeX("Definition of Prior for $Pr(S_1|untested)$"),
       fill ='')

### 2023-07-03 reports/state_figures.Rmd
update figures

# clear labels for versions
versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Emp. Value",
    "$P(S_1|untested)$ Centered at Emp. Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Emp. Value",
         "$P(S_1|untested)$ Centered at Emp. Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ) )
)

>>>>

# clear labels for versions
versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Survey Value",
    "$P(S_1|untested)$ Centered at Survey Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Survey Value",
         "$P(S_1|untested)$ Centered at Survey Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values",
        "$\\beta$ Centered at Survey Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Survey Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ) )
)
